Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2015-03-08 sas2015/content/impl.tex
address reviewer concerns about presentation of efficiency

Both the IFDS and IDE algorithms have been proven
to run in $O(ED^3)$ time~\cite{reps1995precise,sagiv1996precise},
where $E$ is the number of edges in the (non-exploded) supergraph, and $D$ is the size
of the set of facts.
The complexity proof for the IDE algorithm requires the implementation of the micro-functions
to be \textit{efficient} according to the following criteria:
\begin{enumerate}
	\item There is a representation for the identity and top functions.
  \item The representation is closed under the meet and composition operations.
  \item The micro functions form a finite-height lattice.
  \item The apply, meet, composition, and equality-check operations can be computed in constant time.
  \item There is a constant bound on the storage space for a micro function representation.
\end{enumerate}
We prove that the micro-functions for the correlated-call analysis satisfy these
criteria if we consider the number of correlated-call receivers $R$ and the
number of run-time types $T$ constant
(i.e., the operations on micro-functions are allowed to use time that is $O(RT)$,
but constant with respect to $E$ and $D$).

\begin{restatable}{lemma}{efficient}\label{lem:efficient}
  The correlated-call representation of a micro function is efficient if the number of
  correlated-call receivers $\rcc$ and the number of run-time types $T$ are considered constant.
\end{restatable}

From this lemma, we conclude that the correlated-calls analysis runs in time
$O(ED^3\rcc T)$. In other words, the asymptotic cost of the added precision of
the correlated-calls analysis is increased by a factor of $O(\rcc T)$ compared
to the original IFDS analysis.

>>>>

Both the IFDS and IDE algorithms have been proven
to run in $O(ED^3)$ time~\cite{reps1995precise,sagiv1996precise},
where $E$ is the number of edges in the (non-exploded) supergraph, and $D$ is the size
of the set of facts.
The IDE algorithm may evaluate micro-functions up to $O(ED^3)$ times,
so this running time must be multiplied by the cost of evaluating a
micro-function. We show that the micro-functions in the correlated-calls
IDE analysis can be evaluated in time $O(\rcc T)$, where $\rcc$ is the number
of correlated-call receivers $\rcc$ and the $T$ is the number of run-time
types. Therefore, the overall worst-case cost of the correlated-calls IDE analysis
is $O(ED^3\rcc T)$.

Specifically, the complexity proof for the IDE algorithm requires the implementation of the micro-functions
to be \textit{efficient} according to the following criteria:
\begin{enumerate}
	\item There is a representation for the identity and top functions.
  \item The representation is closed under the meet and composition operations.
  \item The micro functions form a finite-height lattice.
  \item The apply, meet, composition, and equality-check operations can be computed in constant time (independent of $E$ and $D$).
  \item There is a constant bound on the storage space for a micro function representation.
\end{enumerate}
We prove these conditions with the following lemma:
\begin{restatable}{lemma}{efficient}\label{lem:efficient}
  The correlated-call representation of a micro function is efficient and the required operations
  on micro-functions can be computed in time $O(\rcc T)$.
\end{restatable}

%From this lemma, we conclude that the correlated-calls analysis runs in time
%$O(ED^3\rcc T)$. In other words, the asymptotic cost of the added precision of
%the correlated-calls analysis is increased by a factor of $O(\rcc T)$ compared
%to the original IFDS analysis.
